---
title: "rMAUPS: Analysis of Ubiquitination"
author:
- name: Collin Tokheim, Wubing Zhang, Jun Ge, X. Shirley Liu
  affiliation: Dana-Farber Cancer Institute
package: "rMAUPS - 0.1.1"
output:
  BiocStyle::html_document
vignette: |
  %\VignetteIndexEntry{rMAUPS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This vignette assumes that you have already properly installed rMAUPS.

# Searching protein sequence

First load in protein sequences from uniprot.

```{r listfile}
datapath <- system.file("extdata", package = "rMAUPS")
uniprot_path <- file.path(datapath, "human_uniprot_seq.txt")
uniprot <- read.delim(uniprot_path, sep='\t')
head(uniprot)
```

Next, search the protein sequences for lysine residues ("K"). 

```{r search}
lysine_pos <- searchProtSeq(head(uniprot), 'K')
head(lysine_pos)
```

Although not used here, the searchProtSeq function can also handle searching for sequences using regular expression.

# Viewing protein structure


# Session info

```{r sessionInfo, echo=FALSE}
sessionInfo()
```
